Fourmile

### 2022-09-20 fourmile_dataprocess.Rmd
solar rad gap filling done

library(rmdformats)
library(tidyverse)
library(dplyr)
library(lubridate)
library(plotly)
library(ggplot2)
library(here)
library(scales)
library(here)
library(rgdal)
library(sp)
library(sf)
library(mapview)
library(kableExtra)
library(dataRetrieval)
library(raster)
library(sf)
library(stringr)
library(hydroGOF)
library(Metrics)
library(ranger)
library(missRanger)
```

@@

```{r}

>>>>

library(rmdformats)
library(tidyverse)
library(dplyr)
library(lubridate)
library(plotly)
library(ggplot2)
library(here)
library(scales)
library(here)
library(rgdal)
library(sp)
library(sf)
library(mapview)
library(kableExtra)
library(dataRetrieval)
library(raster)
library(sf)
library(stringr)
library(hydroGOF)
library(Metrics)
library(ranger)
library(missRanger)
library(readxl)
```

@@

```{r, echo=F}
#bring in srad and niwot_srad
srad_gapfil <- full_join(srad, niwot_srad) %>%
  filter(date > '2009-12-31') %>%
  dplyr::select(-c(prism_w, prism_m, prism_e))

#bat <- read_xlsx('bat_srad.xlsx')
#save.image(file = 'bat.RData')
load('C:/Users/sears/Documents/Repos/fourmile/data/bat.RData')

bet_day <- bat %>%
  mutate(date = as.Date(datetime)) %>%
  group_by(date) %>%
  summarize(sw_in_avg_wm2= mean(in_swrad_wm2)) %>%
  filter(date > '2009-12-31') %>%
  mutate(bet_sw_in_mjm2 = (sw_in_avg_wm2 * 86400) / 1000000) %>%
  dplyr::select(-c(sw_in_avg_wm2))

srad_gapfil_all <- full_join(srad_gapfil, bet_day, by='date') %>%
  filter(date < '2020-12-31') %>%
  dplyr::select(-c(bet_sw_in_mjm2.x)) %>%
  rename(bet_sw = bet_sw_in_mjm2.y)

summary(srad_gapfil_all)

srad_flip_nofill <- srad_gapfil %>%
  pivot_longer(!date, names_to = 'site', values_to = 'sw_in_mjm2')

srad_nofill <- ggplot(srad_flip_nofill, aes(x=date, y=sw_in_mjm2, color=site)) +
  geom_line() +
  ggtitle('Solar rad, no fill')

ggplotly(srad_nofill)

new_srad <- missRanger(srad_gapfil_all, num.trees=100)
summary(new_srad)

srad_flip_fill <- new_srad %>%
  pivot_longer(!date, names_to = 'site', values_to = 'sw_in_mjm2')

srad_filled <- ggplot(srad_flip_fill, aes(x=date, y=sw_in_mjm2, color=site)) +
  geom_line() +
  ggtitle('Solar rad, fill')

ggplotly(srad_filled)
